intro

### 2022-02-17 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd

Every day we are confronted with stressful or emotionally demanding situations. 
The ability to modify emotional experiences, expressions, and physiological reactions [@Gross1998antecedent] to regulate emotions is an important cognitive skill. 
It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning [@Gross1998emerging].
Different strategies <!-- Hier heißt es strategies, später dann tactices, dann wieder strategies. Das sollte vereinheitlicht werden, bzw. muss klar werden ob es einen Unterschied zwischen strategies und tactics gibt und wann das eine oder das andere der korrelte Begrifff ist --> can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification [@Gross1998antecedent], and, following the taxonomy of Powers and LaBar [-@Powers2019], individuals can implement ER strategies by means of different tactics.
So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process [@Gross1998antecedent].
In contrast, response modification takes place late in the process and is therefore conceptualized as a response-focused strategy [@Gross1998antecedent].
This postulated temporal sequence of ER strategies influences their effectiveness.
It is meta-analytically proven that all mentioned strategies reduce subjective emotional arousal [@Webb2012].
Distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed small to medium effect sizes on measures of emotional experience (distraction: _d~+~_ = 0.27; suppression: _d~+~_ = 0.27).
Distancing as tactic of cognitive change showed the highest effectiveness with an effect size of _d~+~_ = 0.45 [@Webb2012].
Moreover it is known that ER strategies reduce physiological arousal, measured via EMG in the region of the *corrugator supercilii* [@Zaehringer2020]. 
So these tactics from three different strategies proved to be effective in the short term. 
However, in order to be able to make a statement on their general benefit, longer-term consequences must also be considered. 
Especially strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
Long-term consequences of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed [@GrossJohn2003]. 
Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of *adaptive* and *maladaptive* strategies.
For example, it could be shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms [@Yoon2013].
Also, a number of ER strategies is linked to psychological disorders (for meta-analytic review, see [@Aldao2010]).

>>>>

Every day we are confronted with stressful or emotionally demanding situations. 
The ability to modify emotional experiences, expressions, and physiological reactions [@Gross1998antecedent] to regulate emotions is an important cognitive skill. 
It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning [@Gross1998emerging].
Different strategies <!-- Ich bin immer noch nicht so richtig dahinter gekommen, was eigentlich der Unterschied zwischen strategies und tactics ist, ich meine, ich weiß, was der Unterschied zwischen einer Strategie und einer Taktik ist, aber inwiefern das in ER eine Rolle spiel, ist mir noch nicht so klar gweorden, aber ich habe auch Powers & LaBar nicht gelesen --> can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification [@Gross1998antecedent], and, following the taxonomy of Powers and LaBar [-@Powers2019], individuals can implement ER strategies by means of different tactics.
So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process [@Gross1998antecedent].
In contrast, response modification takes place late in the process and is therefore conceptualized as a response-focused strategy [@Gross1998antecedent].
This postulated temporal sequence of ER strategies influences their effectiveness.
It is meta-analytically proven that all mentioned strategies reduce subjective emotional arousal [@Webb2012].
Distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed small to medium effect sizes on measures of emotional experience (distraction: _d~+~_ = 0.27; suppression: _d~+~_ = 0.27).
Distancing as tactic of cognitive change showed the highest effectiveness with an effect size of _d~+~_ = 0.45 [@Webb2012].
Moreover it is known that ER strategies reduce physiological arousal, measured via EMG in the region of the *corrugator supercilii* [@Zaehringer2020]. 
So these tactics from three different strategies proved to be effective in the short term. 
However, in order to be able to make a statement on their general benefit, longer-term consequences must also be considered. 
Especially strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
Long-term consequences of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed [@GrossJohn2003]. 
Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of *adaptive* and *maladaptive* strategies.
For example, it could be shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms [@Yoon2013].
Also, a number of ER strategies is linked to psychological disorders (for meta-analytic review, see Aldao et al. [@Aldao2010]).
